---
title: "10C_Graphs_Finaux_1"
author: 
  - Pauline Martinot [UNICOG, NeuroSpin]
  - Bénédicte Colnet [Inria, Paris-Saclay]
date: "1/24/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, include = TRUE)

library(tidyverse)
library(dplyr)
library(rmarkdown)
library(ggplot2)
library(reshape2)
library(alluvial)
library(patchwork)
library(ciTools)
library(gmodels)
library(extrafont)

```

# Parameters to set before launch of the pipeline

```{r}

IMPUTED = "imputed" # "non-imputed"

ANNEE_COHORTE = 2018 # 2018 #2020

```

# Data

```{r}

load(paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_after_2_composite_covariate.RData"))
load(paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_classes.RData"))
load(paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_joined.RData"))
load(paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_joined_n.RData"))
load(paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_joined30_n.RData"))

SEUIL_INF_CLASS = 5

```

# Title : A longitudinal  nation-wide  assessment  of  language  and mathematics in first and second grades

# Graph 1A : Schema Cohorts and Evalaide

# Graph 1B : Age effect on results in Math at T1 and language at T1

Within the total population, do we find higher math and language skills at older ages?

### DATA_AGE 


```{r}

DATA_AGE = data_depp[(data_depp$Age_CP >= 64) & (data_depp$Age_CP <= 86) ,]
DATA_AGE <- DATA_AGE[!is.na(DATA_AGE$Age_Cat) , ]
DATA_AGE$Age_CAT <- case_when(DATA_AGE$Age_Cat == "Young" ~ "Young",
                              DATA_AGE$Age_Cat == "Normal inf" ~ "Normal",
                              DATA_AGE$Age_Cat == "Normal sup" ~ "Normal",
                              DATA_AGE$Age_Cat == "Late" ~ "Late")
DATA_AGE$Age_CAT <- as.factor(DATA_AGE$Age_CAT)

```


### Math x Age colors T1 T2 T3

```{r}
## Math T1

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T1_Math_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  coord_cartesian(ylim=c(20, 72)) +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  xlab("Age in first grade (month)") +
  ylab("Math level at T1 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))



ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Math_T1_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Math T2

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T2_Math_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(20, 72)) +
  xlab("Age in first grade (month)") +
  ylab("Math level at T2 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Math_T2_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Math T3

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T3_Math_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(20, 72)) +
  xlab("Age in first grade (month)") +
  ylab("Math level at T3 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Math_T3_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)



```


### Language x Age effect  T1 T2 T3

```{r echo=TRUE}

# Lang T1 

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T1_Lang_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  coord_cartesian(ylim=c(18,75)) +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  xlab("Age in first grade (month)") +
  ylab("Lang level at T1 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))



ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Lang_T1_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Lang T2

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T2_Lang_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(18, 75)) +
  xlab("Age in first grade (month)") +
  ylab("Lang level at T2 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Lang_T2_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Lang T3

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T3_Lang_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(18, 75)) +
  xlab("Age in first grade (month)") +
  ylab("Lang level at T3 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Lang_T3_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)


```

### Problem Solving x Age effect  T1 T2 T3

```{r echo=TRUE}

# Resoud_Pb T1 

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T1_Resoud_Pb_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  coord_cartesian(ylim=c(25,65)) +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  xlab("Age in first grade (month)") +
  ylab("Resoud_Pb level at T1 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))



ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Resoud_Pb_T1_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Resoud_Pb T2

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T2_Resoud_Pb_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(25, 65)) +
  xlab("Age in first grade (month)") +
  ylab("Resoud_Pb level at T2 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Resoud_Pb_T2_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Resoud_Pb T3

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T3_Resoud_Pb_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(25, 65)) +
  xlab("Age in first grade (month)") +
  ylab("Resoud_Pb level at T3 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Resoud_Pb_T3_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

```

### Number line x Age effect  T1 T2 T3

```{r echo=TRUE}

# Ligne_Num T1 

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T1_Ligne_Num_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  coord_cartesian(ylim=c(30,63)) +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  xlab("Age in first grade (month)") +
  ylab("Ligne_Num level at T1 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))



ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Ligne_Num_T1_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Ligne_Num T2

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T2_Ligne_Num_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(30, 63)) +
  xlab("Age in first grade (month)") +
  ylab("Ligne_Num level at T2 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Ligne_Num_T2_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

# Ligne_Num T3

DATA_AGE %>%
  group_by(Age_CAT) %>%
  ggplot(mapping = aes(x = Age_CP, y = T3_Ligne_Num_P_Rank*100, group = Age_CAT, color = Age_CAT)) +
  stat_summary(fun="mean", size = 4, geom = "point") +
  stat_summary(fun.DATA_AGE="mean_se") +
  scale_color_manual(legend_title,
                     values=c("limegreen", "dodgerblue" , "darkblue" )) +
  coord_cartesian(ylim=c(30, 63)) +
  xlab("Age in first grade (month)") +
  ylab("Ligne_Num level at T3 (percentile rank)") +
  theme_light() +
  theme(axis.line = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.title.y = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))


ggsave(paste0("./img/",ANNEE_COHORTE,"/Graph_1A_Age_Effect_Ligne_Num_T3_", ANNEE_COHORTE,".svg"),
       width = 9, height = 6)

```
### Statistics



```{r echo=TRUE}

#### Stat about School category Class size

# Private + Public
(nrow(data_depp[data_depp$Categ_Etab_CP == "Public" | data_depp$Categ_Etab_CP == "Private", ]) / nrow(data_depp))*100

# Private
DD1 <- data_depp[data_depp$Categ_Etab_CP == "Public", ]
summary(DD1$Taille_Classe)

# Public
DD2 <- data_depp[data_depp$Categ_Etab_CP == "Private", ]
summary(DD2$Taille_Classe)

# REP
DD3 <- data_depp[data_depp$Categ_Etab_CP == "REP", ]
summary(DD3$Taille_Classe)

# REP+
DD4 <- data_depp[data_depp$Categ_Etab_CP == "REP+", ]
summary(DD4$Taille_Classe)

#### Stat about age = proportions

# General

(nrow(data_depp[data_depp$Age_Cat == "Young", ]) / nrow(data_depp))*100
(nrow(data_depp[data_depp$Age_Cat == "Normal inf" | data_depp$Age_Cat == "Normal sup", ]) / nrow(data_depp))*100
(nrow(data_depp[data_depp$Age_Cat == "Late", ]) / nrow(data_depp))*100

#### Stat about age = proportions + Categ

# Private

(nrow(DD1[DD1$Age_Cat == "Young", ]) / nrow(DD1))*100
(nrow(DD1[DD1$Age_Cat == "Normal inf" | DD1$Age_Cat == "Normal sup", ]) / nrow(DD1))*100
(nrow(DD1[DD1$Age_Cat == "Late", ]) / nrow(DD1))*100

# Public
(nrow(DD2[DD2$Age_Cat == "Young", ]) / nrow(DD2))*100
(nrow(DD2[DD2$Age_Cat == "Normal inf" | DD2$Age_Cat == "Normal sup", ]) / nrow(DD2))*100
(nrow(DD2[DD2$Age_Cat == "Late", ]) / nrow(DD2))*100

# REP
(nrow(DD3[DD3$Age_Cat == "Young", ]) / nrow(DD3))*100
(nrow(DD3[DD3$Age_Cat == "Normal inf" | DD3$Age_Cat == "Normal sup", ]) / nrow(DD3))*100
(nrow(DD3[DD3$Age_Cat == "Late", ]) / nrow(DD3))*100

# REP+
(nrow(DD4[DD4$Age_Cat == "Young", ]) / nrow(DD4))*100
(nrow(DD4[DD4$Age_Cat == "Normal inf" | DD4$Age_Cat == "Normal sup", ]) / nrow(DD4))*100
(nrow(DD4[DD4$Age_Cat == "Late", ]) / nrow(DD4))*100


#### Stat about age & Sexe = Proportions

# General Sexe

(nrow(data_depp[data_depp$Sexe == "Boys", ]) / nrow(data_depp))*100
(nrow(data_depp[data_depp$Sexe == "Girls", ]) / nrow(data_depp))*100

# Private

(nrow(DD1[DD1$Sexe == "Boys", ]) / nrow(DD1))*100
(nrow(DD1[DD1$Sexe == "Girls", ]) / nrow(DD1))*100

# Public

(nrow(DD2[DD2$Sexe == "Boys", ]) / nrow(DD2))*100
(nrow(DD2[DD2$Sexe == "Girls", ]) / nrow(DD2))*100

# REP

(nrow(DD3[DD3$Sexe == "Boys", ]) / nrow(DD3))*100
(nrow(DD3[DD3$Sexe == "Girls", ]) / nrow(DD3))*100

# REP+

(nrow(DD4[DD4$Sexe == "Boys", ]) / nrow(DD4))*100
(nrow(DD4[DD4$Sexe == "Girls", ]) / nrow(DD4))*100

##### Stat Age x Sexe


(nrow(data_depp[data_depp$Age_Cat == "Young" & data_depp$Sexe == "Boys", ]) / nrow(data_depp[data_depp$Age_Cat == "Young", ]))*100
(nrow(data_depp[data_depp$Age_Cat == "Young" & data_depp$Sexe == "Girls", ]) / nrow(data_depp[data_depp$Age_Cat == "Young", ]))*100
(nrow(data_depp[(data_depp$Age_Cat == "Normal inf" | data_depp$Age_Cat == "Normal sup") & (data_depp$Sexe == "Boys"), ]) / nrow(data_depp[data_depp$Age_Cat == "Normal inf" | data_depp$Age_Cat == "Normal sup", ]))*100
(nrow(data_depp[(data_depp$Age_Cat == "Normal inf" | data_depp$Age_Cat == "Normal sup") & (data_depp$Sexe == "Girls"), ]) / nrow(data_depp[data_depp$Age_Cat == "Normal inf" | data_depp$Age_Cat == "Normal sup", ]))*100
(nrow(data_depp[(data_depp$Age_Cat == "Late") & (data_depp$Sexe == "Boys"), ]) / nrow(data_depp[data_depp$Age_Cat == "Late", ]))*100
(nrow(data_depp[(data_depp$Age_Cat == "Late") & (data_depp$Sexe == "Girls"), ]) / nrow(data_depp[data_depp$Age_Cat == "Late", ]))*100

```



# Graph 1C : Level x 10 categories and at T1, T2, T3 - TOTAL AGE

### Graph 1C Math x Total age population

```{r}
# Math T1

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T1 = mean(T1_Math_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T1, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(32, 58)) +
  xlab("10 social categories of school") +
  ylab("Math Performance ranks at T1")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Math_10Categ_Total_Math_T1.svg"), width = 6, height = 5)

# Math T2

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T2 = mean(T2_Math_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T2, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(32, 58)) +
  xlab("10 social categories of school") +
  ylab("Math Performance ranks at T2")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Math_10Categ_Total_Math_T2.svg"), width = 6, height = 5)

# Math T3

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T3 = mean(T3_Math_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T3, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(32, 58)) +
  xlab("10 social categories of school") +
  ylab("Math Performance ranks at T3")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Math_10Categ_Total_Math_T3.svg"), width = 6, height = 5)

```


### Graph 1C Language x Total age population

```{r}

# Lang T1

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T1 = mean(T1_Lang_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T1, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(30, 63)) +
  xlab("10 social categories of school") +
  ylab("Lang Performance ranks at T1")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Lang_10Categ_Total_Lang_T1.svg"), width = 9, height = 6, dpi = 150)

# Lang T2

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T2 = mean(T2_Lang_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T2, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(30, 63)) +
  xlab("10 social categories of school") +
  ylab("Lang Performance ranks at T2")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Lang_10Categ_Total_Lang_T2.svg"), width = 9, height = 6, dpi = 150)

# Lang T3

data_depp %>%
  group_by(Categ_10c_CP, Categ_Etab_CP) %>%
  summarise(mean_T3 = mean(T3_Lang_Rank*100)) %>%
  ggplot(aes(x = Categ_10c_CP, y = mean_T3, group = Categ_Etab_CP, color = Categ_10c_CP)) +
  geom_point(size = 4) +
  scale_color_manual(legend_title,
                     values=c("darkblue", "dodgerblue" , "darkgreen", "seagreen", "limegreen",
                              "chartreuse2", "#feb24c" ,"#fd8d3c", "#e31a1c", "darkred")) +
  geom_line(size = 2) +
  coord_cartesian(ylim=c(30, 63)) +
  xlab("10 social categories of school") +
  ylab("Lang Performance ranks at T3")  +
  theme_light() +
  theme(panel.background = element_rect(size = 0.1, linetype = 'solid',
                                colour = "grey")) +
  theme(panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.grid.minor = element_line(size = 0.1, linetype = 'solid',
                                colour = "#CCCCCC")) +
  theme(panel.spacing = unit(2, "lines")) +
  theme(axis.line.x = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.line.y = element_line(arrow = arrow(length = unit(2, "mm")))) +
  theme(axis.title.x = element_text(size=12,  color="black", angle=0, hjust = 1)) +
  theme(axis.text.x = element_text(size=12, color="black", angle=0, hjust = 1)) +
  theme(axis.text.y = element_text(size=12, color="black", angle=0, hjust = 1))

ggsave(paste0("img/",ANNEE_COHORTE,"/Graph_1C_Lang_10Categ_Total_Lang_T3.svg"), width = 9, height = 6, dpi = 150)
```


