---
title: "8_Data_Models_reg"
author:
  - Pauline Martinot [UNICOG, NeuroSpin]
  - Bénédicte Colnet [Inria, Paris-Saclay]
date: "09/01/2022"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
---

# DATA LOADING for all Regression Models

### Parameters

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Parameters to set before launch of the pipeline

ANNEE_COHORTE = "2020" # 2019 #2020
IMPUTED =  "imputed"# "imputed" #"imputed" #"imputed" "non-imputed" 

# Library
library(ggplot2)
library(FactoMineR)
library(dplyr)
library(tidyverse)
library(broom)
library(jtools)
library(LambertW)
library(reshape2)

```

### Data selection

Joined_n : Decision with Benedict to take off children who are in advance or late, as they are very different from the others, while keeping variables with mean per class with their mean.

Selected classes are from 6 to 27 and selection of classes with min 2 boys and 2 girls are for
- joined30_n


```{r}

if(IMPUTED == "imputed"){


load(paste0("./data/cohort_", ANNEE_COHORTE,"_imputed_joined30_n.RData"))
  
  
} 

```

### sanity check 

```{r echo=TRUE}

if(ANNEE_COHORTE == 2018 ){

summary(joined30_n$Taille_Classe)    # min 6 and max 27
summary(joined30_n$n_girls)          # min 2 max 19
summary(joined30_n$n_boy)            # min 2 max 19
summary(joined30_n$boy_proportion)   # 0.30 to 0.70

}

if(ANNEE_COHORTE == 2019 ){

summary(joined30_n$Taille_Classe)    # min 6 and max 27
summary(joined30_n$n_boy)            # min 2 max 19
summary(joined30_n$n_girls)          # min 2 max 18
summary(joined30_n$boy_proportion)   # 0.30 to 0.70

}

if(ANNEE_COHORTE == 2020 ){

summary(joined30_n$Taille_Classe)    # min 6 and max 27
summary(joined30_n$n_boy)            # min 2 max 19
summary(joined30_n$n_girls)          # min 2 max 18
summary(joined30_n$boy_proportion)   # 0.30 to 0.70

}
```


# Rename Sexe_Num as Sexe_Boys for facilitating comprehension when reading results

```{r}

names(joined30_n)[names(joined30_n) == "Sexe_Num"] <- "Sexe_Boys"
joined30_n$Sexe_Boys <- as.numeric(joined30_n$Sexe_Boys)

```

## 1) Gaussianize Variables 

To gaussianize :

- T1_Math, T2_Math, T3_Math
- T1_Language
- IPS_Etab_CP
- Age_CP
- boy_proportion
- Taille_Classe
- First_sexe_in_T1_Math
- First_sexe_in_T1_Language

Keep off the others : "ID_etab_class", "Sexe_Boys"

```{r eval=FALSE, include=FALSE}
joined30_n$Diff_T3_T1_Math_per_class <- as.numeric(joined30_n$T3_Math_mean_per_class - joined30_n$T1_Math_mean_per_class)

joined30_n$Diff_Math_T3_T1_individual <- as.numeric(joined30_n$T3_Math - joined30_n$T1_Math)

joined30_n$Diff_T3_T1_Lang_per_class <- as.numeric(joined30_n$T3_Language_mean_per_class - joined30_n$T1_Language_mean_per_class)

joined30_n$Diff_T3_T1_Lang_individual <- as.numeric(joined30_n$T3_Language - joined30_n$T1_Language)

joined30_n <- joined30_n[ , c("ID_etab_class", "T1_Math", "T2_Math", "T3_Math",
                              "T1_Language", "T2_Language", "T3_Language","IPS_Etab_CP",
                              "Sexe_Boys",
                              "Age_CP", "boy_proportion","Taille_Classe",
                              "First_sexe_in_T1_Math", "First_sexe_in_T1_Language", "Categ_Etab_CP", 
                              "T1_Math_mean_per_class", "T3_Math_mean_per_class",
                              "Diff_T3_T1_Math_per_class", "Diff_Math_T3_T1_individual",
                              "Diff_T3_T1_Lang_per_class", "Diff_T3_T1_Lang_individual")]

```


# Special 2020

```{r}

joined_gau  <- as.data.frame(Gaussianize(joined30_n[, c("T1_Math", "T2_Math", 
                                                        "T1_Language", "T2_Language",
                                                         "IPS_Etab_CP",
                                                        "Age_CP", "boy_proportion","Taille_Classe",
                                                         "First_sexe_in_T1_Math",
                                                        "First_sexe_in_T1_Language",
                                                        "T1_Math_mean_per_class" )],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

names(joined_gau)[names(joined_gau) == "T1_Math.U"]                     <- "T1_Math"
names(joined_gau)[names(joined_gau) == "T2_Math.U"]                     <- "T2_Math"

names(joined_gau)[names(joined_gau) == "T1_Language.U"]                 <- "T1_Language"
names(joined_gau)[names(joined_gau) == "T2_Language.U"]                 <- "T2_Language"

names(joined_gau)[names(joined_gau) == "IPS_Etab_CP.U"]                 <- "IPS_Etab_CP"
names(joined_gau)[names(joined_gau) == "Age_CP.U"]                      <- "Age_CP"
names(joined_gau)[names(joined_gau) == "boy_proportion.U"]              <- "boy_proportion"
names(joined_gau)[names(joined_gau) == "Taille_Classe.U"]               <- "Taille_Classe"
names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Math.U"]       <- "First_sexe_in_T1_Math"
names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Language.U"]   <- "First_sexe_in_T1_Language"
names(joined_gau)[names(joined_gau) == "T1_Math_mean_per_class.U"]      <- "T1_Math_mean_per_class"

joined_gau$T1_Math                     <- as.numeric(joined_gau$T1_Math)
joined_gau$T2_Math                     <- as.numeric(joined_gau$T2_Math)
joined_gau$T1_Language                 <- as.numeric(joined_gau$T1_Language)
joined_gau$T2_Language                 <- as.numeric(joined_gau$T2_Language)
joined_gau$IPS_Etab_CP                 <- as.numeric(joined_gau$IPS_Etab_CP)
joined_gau$Age_CP                      <- as.numeric(joined_gau$Age_CP)
joined_gau$boy_proportion              <- as.numeric(joined_gau$boy_proportion)
joined_gau$Taille_Classe               <- as.numeric(joined_gau$Taille_Classe)
joined_gau$First_sexe_in_T1_Math       <- as.numeric(joined_gau$First_sexe_in_T1_Math)
joined_gau$First_sexe_in_T1_Language   <- as.numeric(joined_gau$First_sexe_in_T1_Language)
joined_gau$T1_Math_mean_per_class      <- as.numeric(joined_gau$T1_Math_mean_per_class)

Base <- joined30_n[, c("ID_etab_class", "Sexe_Boys", "Categ_Etab_CP")]

joined_base_gaussian_3 <- cbind(Base, joined_gau)
rm(Base, joined_gau)

joined_base_gaussian_3$Sexe_Boys <- as.factor(joined_base_gaussian_3$Sexe_Boys)

# 1) compute sd for Math at T1 = Heterogeneity in Math at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Math","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Math")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Math")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.86
sd(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.20

joined_hetero_Math_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_3[, c("heterogeneity_T1_Math")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Math_3$Y1.U) #0
sd(joined_hetero_Math_3$Y1.U) #1

names(joined_hetero_Math_3)[names(joined_hetero_Math_3) == "Y1.U"] <- "heterogeneity_T1_Math_New"

Base <- joined30_n[, c("ID_etab_class")]

rm(heterogeneities, reversed_table)

joined_base_gau_H_3 <- cbind(joined_base_gaussian_3, joined_hetero_Math_3)
names(joined_base_gau_H_3)[names(joined_base_gau_H_3) == "heterogeneity_T1_Math_New"] <- "heterogeneity_T1_Math"

# 1) compute sd for Language at T1 = Heterogeneity in Language at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Language","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Language")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_lang_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Language")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.84
sd(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.18

joined_hetero_Lang_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_lang_3[, c("heterogeneity_T1_Language")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Lang_3$Y1.U) #0
sd(joined_hetero_Lang_3$Y1.U) #1

names(joined_hetero_Lang_3)[names(joined_hetero_Lang_3) == "Y1.U"] <- "heterogeneity_T1_Lang_New"


rm(heterogeneities, reversed_table)

joined_base_gau_Fin_3 <- cbind(joined_base_gau_H_3, joined_hetero_Lang_3)
names(joined_base_gau_Fin_3)[names(joined_base_gau_Fin_3) == "heterogeneity_T1_Lang_New"] <- "heterogeneity_T1_Lang"

rm(joined_base_gaussian_3, joined_base_gau_H_3, joined_base_gau_hetero_3, joined_base_gau_hetero_lang_3, joined_hetero_Lang_3, joined_hetero_Math_3)

Joined_Fin_3 <- joined_base_gau_Fin_3

rm(joined_base_gau_Fin_3)


```



```{r eval=FALSE, include=FALSE}

joined_gau  <- as.data.frame(Gaussianize(joined30_n[, c("T1_Math", "T2_Math", "T3_Math",
                                                        "T1_Language", "T2_Language",
                                                        "T3_Language", "IPS_Etab_CP",
                                                        "Age_CP", "boy_proportion","Taille_Classe",
                                                         "First_sexe_in_T1_Math",
                                                        "First_sexe_in_T1_Language",
                                                        "T1_Math_mean_per_class",
                                                        "T3_Math_mean_per_class",
                                                        "Diff_T3_T1_Math_per_class", 
                                                        "Diff_Math_T3_T1_individual",
                                                        "Diff_T3_T1_Lang_per_class",
                                                        "Diff_T3_T1_Lang_individual")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

```


```{r eval=FALSE, include=FALSE}

names(joined_gau)[names(joined_gau) == "T1_Math.U"]                     <- "T1_Math"
names(joined_gau)[names(joined_gau) == "T2_Math.U"]                     <- "T2_Math"
names(joined_gau)[names(joined_gau) == "T3_Math.U"]                     <- "T3_Math"
names(joined_gau)[names(joined_gau) == "T1_Language.U"]                 <- "T1_Language"
names(joined_gau)[names(joined_gau) == "T2_Language.U"]                 <- "T2_Language"
names(joined_gau)[names(joined_gau) == "T3_Language.U"]                 <- "T3_Language"
names(joined_gau)[names(joined_gau) == "IPS_Etab_CP.U"]                 <- "IPS_Etab_CP"
names(joined_gau)[names(joined_gau) == "Age_CP.U"]                      <- "Age_CP"
names(joined_gau)[names(joined_gau) == "boy_proportion.U"]              <- "boy_proportion"
names(joined_gau)[names(joined_gau) == "Taille_Classe.U"]               <- "Taille_Classe"
names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Math.U"]       <- "First_sexe_in_T1_Math"
names(joined_gau)[names(joined_gau) == "First_sexe_in_T1_Language.U"]   <- "First_sexe_in_T1_Language"
names(joined_gau)[names(joined_gau) == "T1_Math_mean_per_class.U"]      <- "T1_Math_mean_per_class"
names(joined_gau)[names(joined_gau) == "T3_Math_mean_per_class.U"]      <- "T3_Math_mean_per_class"
names(joined_gau)[names(joined_gau) == "Diff_T3_T1_Math_per_class.U"]   <- "Diff_T3_T1_Math_per_class"
names(joined_gau)[names(joined_gau) == "Diff_Math_T3_T1_individual.U"]  <- "Diff_T3_T1_Math_individual"
names(joined_gau)[names(joined_gau) == "Diff_T3_T1_Lang_per_class.U"]   <- "Diff_T3_T1_Lang_per_class"
names(joined_gau)[names(joined_gau) == "Diff_T3_T1_Lang_individual.U"]  <- "Diff_T3_T1_Lang_individual"


joined_gau$T1_Math                     <- as.numeric(joined_gau$T1_Math)
joined_gau$T2_Math                     <- as.numeric(joined_gau$T2_Math)
joined_gau$T3_Math                     <- as.numeric(joined_gau$T3_Math)
joined_gau$T1_Language                 <- as.numeric(joined_gau$T1_Language)
joined_gau$T2_Language                 <- as.numeric(joined_gau$T2_Language)
joined_gau$T3_Language                 <- as.numeric(joined_gau$T3_Language)
joined_gau$IPS_Etab_CP                 <- as.numeric(joined_gau$IPS_Etab_CP)
joined_gau$Age_CP                      <- as.numeric(joined_gau$Age_CP)
joined_gau$boy_proportion              <- as.numeric(joined_gau$boy_proportion)
joined_gau$Taille_Classe               <- as.numeric(joined_gau$Taille_Classe)
joined_gau$First_sexe_in_T1_Math       <- as.numeric(joined_gau$First_sexe_in_T1_Math)
joined_gau$First_sexe_in_T1_Language   <- as.numeric(joined_gau$First_sexe_in_T1_Language)
joined_gau$T1_Math_mean_per_class      <- as.numeric(joined_gau$T1_Math_mean_per_class)
joined_gau$T3_Math_mean_per_class      <- as.numeric(joined_gau$T3_Math_mean_per_class)
joined_gau$Diff_T3_T1_Math_per_class   <- as.numeric(joined_gau$Diff_T3_T1_Math_per_class)
joined_gau$Diff_T3_T1_Math_individual  <- as.numeric(joined_gau$Diff_T3_T1_Math_individual)
joined_gau$Diff_T3_T1_Lang_per_class   <- as.numeric(joined_gau$Diff_T3_T1_Lang_per_class)
joined_gau$Diff_T3_T1_Lang_individual  <- as.numeric(joined_gau$Diff_T3_T1_Lang_individual)

```

## 2) Add Gaussianize and non Gaussianized

```{r eval=FALSE, include=FALSE}

Base <- joined30_n[, c("ID_etab_class", "Sexe_Boys", "Categ_Etab_CP")]

joined_base_gaussian_3 <- cbind(Base, joined_gau)
rm(Base, joined_gau)

joined_base_gaussian_3$Sexe_Boys <- as.factor(joined_base_gaussian_3$Sexe_Boys)

```

## 3) Heterogeneity

After T1_Math is gaussianized  => create Heterogeneity_T1_Math and Heterogeneity_T1_Language

```{r eval=FALSE, include=FALSE}


# 1) compute sd for Math at T1 = Heterogeneity in Math at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Math","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Math")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Math")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.86
sd(joined_base_gau_hetero_3$heterogeneity_T1_Math) #0.20

joined_hetero_Math_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_3[, c("heterogeneity_T1_Math")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Math_3$Y1.U) #0
sd(joined_hetero_Math_3$Y1.U) #1

names(joined_hetero_Math_3)[names(joined_hetero_Math_3) == "Y1.U"] <- "heterogeneity_T1_Math_New"

Base <- joined30_n[, c("ID_etab_class")]

rm(heterogeneities, reversed_table)

joined_base_gau_H_3 <- cbind(joined_base_gaussian_3, joined_hetero_Math_3)
names(joined_base_gau_H_3)[names(joined_base_gau_H_3) == "heterogeneity_T1_Math_New"] <- "heterogeneity_T1_Math"

# 1) compute sd for Language at T1 = Heterogeneity in Language at T1

reversed_table <- melt(joined_base_gaussian_3[, c("T1_Language","ID_etab_class")], id = c("ID_etab_class"))
heterogeneities <- dcast(reversed_table, ID_etab_class ~ variable, sd)
names(heterogeneities) <- c("ID_etab_class", paste0("heterogeneity_",  c("T1_Language")))

# merge heterogeneities and main classes table
joined_base_gau_hetero_lang_3 <- merge(joined_base_gaussian_3, heterogeneities[ , c("ID_etab_class", "heterogeneity_T1_Language")],
                 by = "ID_etab_class")

mean(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.84
sd(joined_base_gau_hetero_lang_3$heterogeneity_T1_Language) #0.18

joined_hetero_Lang_3  <- as.data.frame(Gaussianize(joined_base_gau_hetero_lang_3[, c("heterogeneity_T1_Language")],
                                         type = c("s"), method = c("IGMM"), return.u = TRUE))

mean(joined_hetero_Lang_3$Y1.U) #0
sd(joined_hetero_Lang_3$Y1.U) #1

names(joined_hetero_Lang_3)[names(joined_hetero_Lang_3) == "Y1.U"] <- "heterogeneity_T1_Lang_New"


rm(heterogeneities, reversed_table)

joined_base_gau_Fin_3 <- cbind(joined_base_gau_H_3, joined_hetero_Lang_3)
names(joined_base_gau_Fin_3)[names(joined_base_gau_Fin_3) == "heterogeneity_T1_Lang_New"] <- "heterogeneity_T1_Lang"

rm(joined_base_gaussian_3, joined_base_gau_H_3, joined_base_gau_hetero_3, joined_base_gau_hetero_lang_3, joined_hetero_Lang_3, joined_hetero_Math_3)

Joined_Fin_3 <- joined_base_gau_Fin_3

rm(joined_base_gau_Fin_3)

```



## 4) Private Public & REP REP+

```{r eval=FALSE, include=FALSE}

# when drawing graphs, we note children being in advance or late when entering first grade are not following the same patterns than children who entered in first grade at the normal age. Therefore, we selected here only children being in the scope of normal age, while keeping the informations about who's first of class and class's means.

# Joined_Fin_3

join_n_PP_3 <- Joined_Fin_3[Joined_Fin_3$Categ_Etab_CP == "Public" | Joined_Fin_3$Categ_Etab_CP == "Private", ]
join_n_RR_3 <- Joined_Fin_3[Joined_Fin_3$Categ_Etab_CP == "REP" | Joined_Fin_3$Categ_Etab_CP == "REP+", ]


```


## 5) Save DATA

classes ( > 5 to < 28 per class) 

& min 30% boys or min 30% girls

& min 2 boys and min 2 girls in a class of 6 students.


```{r}

save.image(file = paste0("./data/cohort_", ANNEE_COHORTE, "_", IMPUTED, "_ModRegLin_Article.RData"))


```


