---
title: "Multiniveaux 2 aleatoires"
author: "Pauline MARTINOT"
date: "12/10/2021"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  pJoined_Fin_3_document:
    toc: yes
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 2
abstract: |
  This notebook concerns Multi level analysis of DEPP
---

## Load DATA 

Selected classes are 
- from 6 to 27 children per class
- at least 2 boys and 2 girls per class
- minimum with 30% of boys or 30% of girls
- with normal Age in first grade (69 to 80 mo included)

```{r}
knitr::opts_chunk$set(echo = TRUE)

# Parameters to set before launch of the pipeline

ANNEE_COHORTE = "2018" # 2019 #2020

library(tidyverse)
library(dplyr)
library(reshape2)
library(MatchIt)
library(patchwork)
library(lmerTest)
library(glmertree)
library(performance)
library(broom)


load(file = paste0("./data/cohort_", ANNEE_COHORTE, "_imputed_ModRegLin_Article.RData"))


```


# Math models 

# 1) T3 Math Gender gap _ Final model


```{r}

model1 <- lmer(T3_Math ~

                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Math +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Math +
                 
                 Sexe_Boys*Age_CP +
                 Sexe_Boys*T1_Math +
                 Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Math +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion+
                 Sexe_Boys*heterogeneity_T1_Math +
                 
               

                 (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))

write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Model8_Final.csv"), row.names = F)

```



# 2) T1 Math


```{r}

model1 <- lmer(T1_Math ~

                 Age_CP +
                 Sexe_Boys +
                 # T1_Language +

                 First_sexe_in_T1_Math +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 
                 Sexe_Boys*Age_CP +
                 # Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Math +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion +
                   
                 (1 + Sexe_Boys | ID_etab_class),
               data = Joined_Fin_3,  REML = FALSE)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T1_Math_final.csv"), row.names = F)
rm(model1, m1)

```




# 3) T2 Math


```{r}

model1 <- lmer(T2_Math ~

                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Math +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Math +

                 Sexe_Boys*Age_CP +
                 Sexe_Boys*T1_Math +
                 Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Math +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion+
                 Sexe_Boys*heterogeneity_T1_Math +
                 
                   
                 (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T2_Math_Final.csv"), row.names = F)
rm(model1, m1)

```





# 4) T3 Math empty and progressive models


```{r eval=FALSE, include=FALSE}

model1 <- lmer(T3_Math ~ 1 + (1 | ID_etab_class),
                 data = Joined_Fin_3,  REML = FALSE)
summary(model1)
m1 <- coef(summary(model1))
m1
# write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Class.csv"), row.names = F)

model2 <- lmer(T3_Math ~ 1 + (1 + T1_Math | ID_etab_class),
                 data = Joined_Fin_3,  REML = FALSE)
summary(model2)
m2 <- coef(summary(model2))
m2
# write.csv2(m2, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Simple_m4.csv"), row.names = F)

model3 <- lmer(T3_Math ~ 1 + (1 + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model3)
m3 <- coef(summary(model3))
m3
# write.csv2(m3, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_GenderSexe.csv"), row.names = F)

model4 <- lmer(T3_Math ~ T1_Math + (1 + T1_Math | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model4)
m4 <- coef(summary(model4))
m4
# write.csv2(m4, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Math.csv"), row.names = F)

model5 <- lmer(T3_Math ~ Sexe_Boys + (1 + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model5)
m5 <- coef(summary(model5))
m5
# write.csv2(m4, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_Empty_Math.csv"), row.names = F)

model6 <- lmer(T3_Math ~ 1 + (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model6)
m6 <- coef(summary(model6))
# write.csv2(m6, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod1.csv"), row.names = F)

rm(model1, model2, model3, model4, model5, model6)
rm(m1, m2, m3, m4, m5, m6)

# empty interactions

model1 <- lmer(T3_Math ~ T1_Math*Sexe_Boys +
                 (1 | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model1)
m1 <- coef(summary(model1))
m1

# empty interaction + T1Math random

model2 <- lmer(T3_Math ~
                 Sexe_Boys*T1_Math +
                 (1 + T1_Math | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model2)
m2 <- coef(summary(model2))
m2

# empty interaction + Sexe random

model3 <- lmer(T3_Math ~
                 Sexe_Boys*T1_Math +
                 (1 + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model3)
m3 <- coef(summary(model3))
m3

# empty interaction + T1 math and Sexe random

model4 <- lmer(T3_Math ~
                 Sexe_Boys*T1_Math +
                 (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)
summary(model4)
m4 <- coef(summary(model4))
m4

### B. T3 Math = var indiv

model2 <- lmer(T3_Math ~ 
                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +
                 (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model2)
m2 <- coef(summary(model2))
# write.csv2(m2, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod2.csv"), row.names = F)

rm( m2)


### C. T3 Math = var indiv + var collec

model2 <- lmer(T3_Math ~ 
                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Math +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Math +
                 
                 (1 + T1_Math + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model2)
m2 <- coef(summary(model2))
# write.csv2(m2, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_Math_n_Mod3.csv"), row.names = F)

rm( m2)

```

# Language models

#1) T3 Lang Gender gap _ Final model


```{r}

model1 <- lmer(T3_Language ~

                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Lang +
                 
                 Sexe_Boys*Age_CP +
                 Sexe_Boys*T1_Math +
                 Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Language +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion+
                 Sexe_Boys*heterogeneity_T1_Lang +

                 (1 + T1_Language + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))

write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_LANG_Model9_Final.csv"), row.names = F)



```


# 2) T1 Lang


```{r}

model1 <- lmer(T1_Language ~

                 Age_CP +
                 Sexe_Boys +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 
                 Sexe_Boys*Age_CP +
                 Sexe_Boys*First_sexe_in_T1_Language +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion +
                   
                 (1 + Sexe_Boys | ID_etab_class),
               data = Joined_Fin_3,  REML = FALSE)
               
summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T1_LANG_Final.csv"), row.names = F)
rm(model1, m1)

```




# 3) T2 Lang


```{r}

model1 <- lmer(T2_Language ~

                 Age_CP +
                 Sexe_Boys +
                 T1_Math +
                 T1_Language +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Lang +

                 Sexe_Boys*Age_CP +
                 Sexe_Boys*T1_Math +
                 Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Language +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion+
                 Sexe_Boys*heterogeneity_T1_Lang +
                 

                   
                 (1 + T1_Language + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))
m1
write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T2_LANG_Final.csv"), row.names = F)
rm(model1, m1)

```

#4) T3 Lang Gender gap _ with lang T3-T1 class and individual


```{r}

model1 <- lmer(T3_Language ~

                 Age_CP +
                 Sexe_Boys +
                 T1_Math +

                 First_sexe_in_T1_Language +
                 IPS_Etab_CP +
                 Taille_Classe +
                 boy_proportion +
                 heterogeneity_T1_Lang +
                 Diff_T3_T1_Lang_per_class +
                 Diff_T3_T1_Lang_individual +
                 
                 Sexe_Boys*Age_CP +
                 Sexe_Boys*T1_Language +
                 Sexe_Boys*First_sexe_in_T1_Language +
                 Sexe_Boys*IPS_Etab_CP +
                 Sexe_Boys*Taille_Classe +
                 Sexe_Boys*boy_proportion+
                 Sexe_Boys*heterogeneity_T1_Lang +
                 Sexe_Boys*Diff_T3_T1_Lang_per_class +
                 Sexe_Boys*Diff_T3_T1_Lang_individual +
                 
               

                 (1 + Sexe_Boys | ID_etab_class), 
                 data = Joined_Fin_3,  REML = FALSE)

summary(model1)
m1 <- coef(summary(model1))

write.csv2(m1, file= paste0("./table/MultiLevel_Model_", ANNEE_COHORTE, "_T3_LANG_Model10_Final_additional.csv"), row.names = F)



```